Software Product Line Analysis Techniques

### 2018-01-06 doc/quals/quals.tex
SuperC

\section{SuperC}
\cite{Gazzillo:2012}

@@

>>>>

@@

\section{SuperC}
In \cite{Gazzillo:2012}, a variability-aware C-language parser and preprocessor are presented and evaluated against a similar C parser implemented as a part of the TypeChef project \cite{Kastner:2011}. SuperC includes a lexer, a preprocessor and a Fork Merge LR (FMLR) parser. Several optimizations have been implemented to lower the number of forked subparsers, and consequently speedup parsing. On the x86 Linux kernel codebase, SuperC is 3.4 to 3.8 times faster than TypeChef.

The idea behind FMLR parsing is to fork subparsers (initially sharing the state of their parent) on each variability point. A naive implementation would result in a number of subparsers exponential in the number of variability features. To prevent this exponential explosion, SuperC implements 4 optimizations: follow-set calculation, early reduces, lazy shifts, and shared reduces. With those optimizations, for almost all the Linux kernel compilation units the number of subparsers is less than 20.

In addition to the optimizations, SuperC uses Binary Decision Diagrams (BDDs) to encode and test the satisfiability of presence conditions, while TypeChef uses a SAT-solver. Presence conditions are conjuncted on the nesting of static conditional compilation directives, and disjuncted on merges. With a few (tens) of propositional variables, conjunction and disjunction of BDDs is typically more efficient than applying the same operations to CNF-encoded boolean formulas (processed by SAT-solvers). As a result, BDDs also contribute to SuperC's speedup compared to TypeChef.

Another advantage of SuperC compared to TypeChef is that the SuperC preprocessor and parser take into account the possible interactions between different preprocessing and parsing rules of the C language. TypeChef misses some of those interactions (and also some non-standard preprocessing directives), which is the reason why it fails to parse thousands of the Linux kernel source files. SuperC on the other hand parses the whole codebase.
